# 1. BUSINESS UNDERSTANDING
## a. Defining the question
## b. Defining the metric of success
## c. Understading the context
## d. Recording the experimental design
## e. Data Relevance
## f. Appropriateness of the data
# 2. DATA AQUISITION AND EXTRACTION, TRANSFORMING AND LOADING
## a. Importing of the libraries
```{r}
library(data.table)
```
## b. Reading the dataset

```{r}
clo <- fread('http://bit.ly/EcommerceCustomersDataset')
```

```{r}
head(clo, 10)
```
```{r}
tail(clo,10)
```
##c. Checking the dataset
```{r}
dim(clo)
```
```{r}
print(colnames(clo))
```
```{r}
summary(clo)
```
## d. Data understanding
```{r}
majinazacolumns <- colnames(clo)
madarasazacolumns <- c()
eunikiwacolumn <- c()
for (r in majinazacolumns){
  madarasazacolumns <- c(madarasazacolumns , class(clo[[r]]))
  eunikiwacolumn <- c(eunikiwacolumn , length(unique(clo[[r]])))
}

desc <- data.frame(
  "Column name" = majinazacolumns,
  "Data Type" = madarasazacolumns,
  "Number of unique columns" = eunikiwacolumn 
)
desc
```
Administrative - This is a numerical representation of the site.
Administrative_Duration - The amount of time that is spent on the site
Informational - A numerical representation of a site that has information
Informational_Duration - The amount of time that is spent on the information site
ProductRelated - A numerical representation of the site that has the product information
ProductRelated_Duration  - The amount of time that is spent on the product information site.
BounceRates 
ExitRates 
PageValues 
SpecialDay 
Month -
OperatingSystems -  
Browser -
Region 
TrafficType 
VisitorType 
Weekend 
Revenue 


## e. Data preparation
### Data Cleaning
####  i.) Missing Data
```{r}
colSums(is.na(clo))
```
```{r}
clo <- na.omit(clo)
```
#### ii.) Duplicate handling
```{r}
col <- unique(clo)
```
#### iii.) Obvious Inconsistencies








```{r}
mezayanambari <- desc[desc$Data.Type == 'integer' | desc$Data.Type == 'numeric',]
print(mezayanambari)
```

```{r}
clo[clo$Administrative_Duration == -1]
```

```{r}
negativecheck = c('Administrative_Duration', 'Informational_Duration' , 'ProductRelated_Duration')
w = negativecheck
for (b in 1:3){
  wer = clo[clo$w[b] != -1]
  cat ('Dropped: ' , w[b], '\n')
  w1 = w[-b]
  print (dim(wer[wer$w1[1] != 1]))
  print (dim(wer[wer$w1[2] != 1]))
  cat('\n')
}
```
##f. Anomalies
```{r}
tofactor <- c('OperatingSystems', 'Browser', 'Region', 'TrafficType', 'Administrative', 'Informational', 'ProductRelated')
for (lk in tofactor){
  clo[[lk]] <- as.factor(clo[[lk]])
}
```

```{r}
majinazacolumns <- colnames(clo)
madarasazacolumns <- c()
eunikiwacolumn <- c()
for (r in majinazacolumns){
  madarasazacolumns <- c(madarasazacolumns , class(clo[[r]]))
  eunikiwacolumn <- c(eunikiwacolumn , length(unique(clo[[r]])))
}

desc <- data.frame(
  "Column name" = majinazacolumns,
  "Data Type" = madarasazacolumns,
  "Number of unique columns" = eunikiwacolumn 
)
desc
```
## g. Outliers
```{r}
mezayanambari <- desc[desc$Data.Type == 'integer' | desc$Data.Type == 'numeric',]
nambari = mezayanambari$Column.name
for (t in nambari){
  boxplot(col[[t]] , main = t)
}

```
## g. Exploratory Data Analysis
### i.) Univariate Data Analysis
```{r}
#central tendency

numericalcolumns <- mezayanambari$Column.name
centr <- data.frame(
	'Mean' = apply(clo[, ..numericalcolumns] , 2 , mean),
	'Median' = apply(clo[, ..numericalcolumns], 2 , median),
	#Mode = apply(dt[,1:4], 2 , mode),
	'Maximum' = apply(clo[, ..numericalcolumns], 2 , max),
	'Minimum' = apply(clo[, ..numericalcolumns], 2 , min),
	'Standard Deviation' = apply(clo[, ..numericalcolumns], 2 , sd),
	'Variance' = apply(clo[, ..numericalcolumns], 2 , var)
	)
centr
```
### ii.) Bivariate Data Analysis
### iii.) Multivariate Data Analysis

# 3. MODELLING
